### 2019-06-08 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits.tex
Lots of small typos.

We introduce additional notations in the following definition.
%
\begin{definition}\label{def:5:nbSelections_nbCollisions}
\begin{leftbar}[defnbar]  % XXX leftbar defnbar, comment if needed
  % [$T_k(T)$ and $\cC_k(T)$]
  % \label{def:5:nbSelections}
  Let $T^j_k(T) \eqdef \sum_{t=1}^T \indic(A^j(t) = k)$,
  and denote $T_k(T) \eqdef \sum_{j=1}^M T^j_k(T)$ the \emph{number of selections} of arm $k\in[K]$ by any player $j\in[M]$, up to time $T$.
  % and $\cC_k(T)$ be the number of collisions on arm $k$ up-to time $T$.
% \end{definition}

@@

\begin{lemma}\label{lem:5:DecompositionRegret}
\begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
  For any bandit instance $\boldsymbol{\mu}\in\cP_M$ such that $\mu_M^* > \mu_{M+1}^*$, it holds that
  % \vspace*{-5pt}  % XXX
  % \begin{small}
    \begin{align}\label{eq:5:termeundeuxtermetrois}
      R_T(\boldsymbol{\mu}, M, \cA) &=
      \underbrace{\sum_{k \in \Mworst} (\mu_M^* -  \mu_k) \E_{\mu}[T_k(T)]}_{\emph{\mytag{(a)}{eq:5:term1}}} \\
      & \;\;\;\;\;\;
      + \;\; \underbrace{\sum_{k \in \Mbest} (\mu_k -  \mu_M^*) (T - \E_{\mu}[T_k(T)])}_{\emph{\mytag{(b)}{eq:5:term2}}}
      + \;\; \underbrace{\sum_{k=1}^{K} \mu_k \E_{\mu}[\cC_k(T)]}_{\emph{\mytag{(c)}{eq:5:term3}}}. \nonumber
    \end{align}
  % \end{small}
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}

@@

  Using the definition of regret $R_T$ from \eqref{eq:5:regret}, and this collision indicator $\eta^j(t) \eqdef \indic(\overline{C^j(t)})$,

@@

    R(T)

@@

      - \sum_{k=1}^{K} \sum_{j=1}^{M} \mu_k \E_{\mu}\left[ T^j_k(T) \right]

@@

    \intertext{For the first term, we have $T M = \sum\limits_{k=1}^{K} \sum\limits_{j=1}^{M} \E_{\mu}\left[ T^j_k(T)\right]$, and if we denote $\overline{\mu}^* \eqdef \frac{1}{M} \sum\limits_{j \in \Mbest} \mu_j$ the average mean of the $M$-best arms, then,}

@@

    &= \sum_{k=1}^{K} \sum_{j=1}^{M} (\overline{\mu}^* - \mu_k) \E_{\mu}\left[ T^j_k(T) \right]

@@

    &= \sum_{k \in \Mbest\setminus\{M\}} \overline{\Delta_k} \E_{\mu}\left[ T_k(T) \right]
      + \overline{\Delta_{M^*}} \E_{\mu}\left[ T_{M^*}(T) \right] \\
      &\;\;\;\;\;\;\;\; + \sum_{k \in \Mworst} \overline{\Delta_k} \E_{\mu}\left[ T_k(T) \right]

@@

    \intertext{But for $k = M^*$, $T_{M^*}(T) = T M^* - \sum\limits_{k \in \Mbest\setminus\{M\}} \E_{\mu}\left[ T_k(T) \right] - \sum\limits_{k \in \Mworst} \E_{\mu}\left[ T_k(T) \right]$, so by recombining the terms, we obtain,}

@@

    &= \sum_{k \in \Mbest\setminus\{M\}} (\overline{\Delta_k} - \overline{\Delta_{M^*}}) \E_{\mu}\left[ T_k(T) \right]

@@

      &\;\;\;\;\;\;\;\; + \sum_{k \in \Mworst} (\overline{\Delta_k} - \overline{\Delta_{M^*}}) \E_{\mu}\left[ T_k(T) \right]

@@

    R(T)
    &= \sum_{k \in \Mbest} (\mu_{M^*} - \mu_k) \E_{\mu}\left[ T_k(T) \right]

@@

      &\;\;\;\;\;\;\;\; + \sum_{k \in \Mworst} (\mu_{M^*} - \mu_k) \E_{\mu}\left[ T_k(T) \right]

@@

  R(T)
    & = \sum_{k \in \Mbest} (\mu_k - \mu_{M^*}) \left(T - \E_{\mu}\left[ T_k(T) \right]\right) \\
      & \;\; + \sum_{k \in \Mworst} (\mu_{M^*} - \mu_k) \E_{\mu}\left[ T_k(T) \right]

@@

The regret decomposition in Lemma~\ref{lem:5:DecompositionRegret} is valid for both centralized and decentralized algorithms.
For centralized algorithms, due to the absence of collisions, \ref{eq:5:term3} is obviously zero, and \ref{eq:5:term2} is non-negative, as $T_k(T) \leq T$. For decentralized algorithms, \ref{eq:5:term3} may be significantly large, and term \ref{eq:5:term2} may be negative, as many collisions on arm $k$ may lead to $T_k(T) > T$ (which is counter intuitive with such notations).
However, a careful manipulation of this decomposition shows that the regret is always lower bounded by term \ref{eq:5:term1}.
The Figure~\ref{fig:5:MP__M9_K9_T10000_N1000__9_algos__main_RegretCentralized____env6} in Appendix illustrate two cases of $M<K$ and $M=K$ and the different impact of the three terms (\ref{eq:5:term1}, \ref{eq:5:term2} and \ref{eq:5:term3}) on the regret.

\begin{lemma}\label{lem:5:1stLowerBound}
\begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
    For any strategy $\cA$ and $\boldsymbol{\mu}\in\cP_M$, it holds that
    \begin{align*}
        R_T(\boldsymbol{\mu}, M, \cA)    \geq \sum\limits_{k \in \Mworst} (\mu_M^*- \mu_k) \E_{\mu}[T_k(T)].
    \end{align*}
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}

\begin{smallproof}
  Note that term \ref{eq:5:term3} is clearly lower bounded by $0$
  but it is not obvious for \ref{eq:5:term2} as there is no reason for $T_k(T)$ to be upper bounded by $T$.
  %
  Let $T_k^{!}(T) \eqdef \sum_{t=1}^{T} \indic(\exists! j, A^j(t)=k)$,
  where the notation $\exists!$ stands for ``there exists a unique''.
  Then $T_k(T) = \sum_{t=1}^{T} \sum_{j=1}^{M} \indic(A^j(t) = k)$ can be decomposed as
  \begin{equation*}
    T_k(T) = \sum_{t=1}^{T} \indic(\exists! j, A^j(t) = k) + \sum_{t=1}^{T} \sum_{j=1}^{M} c_{k,t} \indic(A^j(t) = k)
    = T_k^{!}(T) + C_k(T).
  \end{equation*}
  By focusing on the two terms $\ref{eq:5:term2} + \ref{eq:5:term3}$ from the decomposition of $R_T(\boldsymbol{\mu}, M, \cA)$ from Lemma~\ref{lem:5:DecompositionRegret}, we have
  \begin{align*}
    \ref{eq:5:term2} + \ref{eq:5:term3} &=
    \sum_{k \in \Mbest} (\mu_k - \mu_M^*) (T - \E_{\mu}[T_k^!(T)])
    + \sum_{k \in \Mbest} \mu_M^* \E_{\mu}[C_k(T)] \\
    & \;\;\;\;\;\; + \sum_{k=1}^{M} \mu_k \E_{\mu}[C_k(T)]
    - \sum_{k \in \Mbest} \mu_k \E_{\mu}[C_k(T)] \\
    &=
    \sum_{k \in \Mbest} (\mu_k - \mu_M^*) (T - \E_{\mu}[T_k^!(T)])
    + \sum_{k \in \Mbest} \mu_M^* \E_{\mu}[C_k(T)]
    + \sum_{k \in \Mworst} \mu_k \E_{\mu}[C_k(T)] \\
    &=
    \sum_{k \in \Mbest} (\mu_k - \mu_M^*) (T - \E_{\mu}[T_k^!(T)])
    + \sum_{k=1}^{M} \min(\mu_M^*, \mu_k) \E_{\mu}[C_k(T)].
  \end{align*}
  And now both terms are non-negative, as $T_k^!(T) \leq T$, $\min(\mu_M^*, \mu_k)\geq 0$, and $C_k(T) \geq 0$, so $\ref{eq:5:term2} + \ref{eq:5:term3} \geq 0$
  which proves that $R_T(\boldsymbol{\mu}, M, \cA) \geq \ref{eq:5:term1}$, as wanted.
\end{smallproof}

@@

\begin{definition}\label{def:5:DecentralizedUniformEfficiency}
\begin{leftbar}[defnbar]  % XXX leftbar defnbar, comment if needed
  An algorithm $\cA$  is \emph{\textbf{strongly uniformly efficient}} if for all $\boldsymbol{\mu} \in \cP_M$ and for all $\alpha \in (0,1)$,
  % \vspace*{-5pt}  % XXX
  \begin{align}
    & R_T(\boldsymbol{\mu},M,\cA) \mathop{=}\limits_{T \to +\infty} o(T^\alpha) \\
    \text{and} & \;
    \forall j \in [M], k \in \Mbest, \;\;
    % a_{j,k}
    \frac{T}{M}
    - \E_{\mu}[T^j_k(T)] \mathop{=}\limits_{T \to +\infty} o(T^{\alpha}).
    \label{eq:5:SUE}
  \end{align}
\end{leftbar}  % XXX leftbar defnbar, comment if needed
\end{definition}

Having a small regret on every problem instance, \ie, being uniformly efficient,
is a natural assumption,
that rules out algorithms tuned to perform well on specific instances only (\eg, fixed-armed algorithms).
%
From this assumption $\left(R_T(\boldsymbol{\mu},M,\cA)=o(T^\alpha)\right)$ and the decomposition of Lemma~\ref{lem:5:DecompositionRegret} one can see\footnote{With some arguments used in the proof of Lemma~\ref{lem:5:1stLowerBound} to circumvent the fact that \ref{eq:5:term2} may be negative.} that for every $k \in \Mbest$,
${T}- \E_{\mu}[T_k(T)] {=} o(T^{\alpha})$, and so
\begin{equation}\label{eq:5:intermediate}
  % \vspace*{-5pt}  % XXX
  \sum_{j =1}^M\left(\frac{T}{M} - \E_{\mu}[T^j_k(T)]\right) = o(T^{\alpha}).
  % \vspace*{-5pt}  % XXX
\end{equation}

The additional assumption in \eqref{eq:5:SUE} further implies some notion of \emph{fairness}, as it suggests that each of the $M$ players spends on average the same amount of time on each of the $M$ best arms. Note that this assumption is satisfied by any strategy that is invariant under every permutation of the players, \ie, for which the distribution of the observations under $\cA_{\sigma} = (\cA_{\sigma(1)},\dots,\cA_{\sigma(M)})$ is independent from the choice of permutation $\sigma \in \Sigma_M$ of the set $\{1,\dots,M\}$.
In that case, it holds that  $\E_{\mu}[T_k^j(T)]=\E_{\mu}[T_k^{j'}(T)]$ for every arm $k$ and $(j,j') \in [M]$, hence \eqref{eq:5:SUE} and \eqref{eq:5:intermediate} are equivalent, and strong uniform efficiency is equivalent to standard uniform efficiency.
Note that the algorithms studied in Section~\ref{sec:5:algorithms} are permutation invariant, and \MCTopM-\klUCB{} is thus an example of strongly uniformly efficient algorithm, as we prove in Section~\ref{sec:5:upperbounds} that its regret is logarithmic on every instance $\mu \in \cP_M$.

@@

\begin{theorem}\label{thm:5:BetterLowerBound}
\begin{leftbar}[theorembar]  % XXX leftbar theorembar, comment if needed
  Under observation models $\modelun$ and $\modeldeux$, consider a strongly uniformly efficient \emph{decentralized} policy $\cA=(\cA_1,\dots,\cA_M)$ and a problem $\boldsymbol{\mu}\in\cP_M$.
  Furthermore, if $\cA_j$ satisfies $\cI_{\bm{\mu},\bm{\lambda}}(\cA_j,T) = \smallO{\log(T)}$, then
  % \vspace*{-10pt}  % XXX
  \begin{equation}\label{eq:5:LBDraws}
    \forall j \in [M], \ \forall k \in \Mworst, \ \ \ \liminf_{T\to \infty} \frac{\E_{\mu}[T_k^j(T)]}{\log(T)} \geq \frac{1}{\kl(\mu_k, \mu_M^*)}.
  \end{equation}

@@

Observe that the regret lower bound \eqref{eq:5:ourLowerBound} is tighter than the state-of-the-art lower bound in this setup
given by \cite{Zhao10}, that states that
\begin{equation}\label{eq:5:Zhao10LowerBound}
  \mathop{\lim\inf}\limits_{T \to +\infty} \frac{R_T(\boldsymbol{\mu}, M, \cA)}{\log(T)}
  \geq \sum_{k \in \Mworst} \left( \sum_{j=1}^{M} \frac{(\mu_M^* -  \mu_k)}{\kl(\mu_k, \mu_{j}^*)} \right),
\end{equation}
as for every $k \in \Mworst$ and $j \in [M]$, $\kl(\mu_k, \mu_j^*) \geq \kl(\mu_k, \mu_M^*)$
(see Figure~\ref{fig:5:CompLowerBounds} in Appendix~\ref{app:5:illustrationLowerBound}).
%
It is worth mentioning that \cite{Zhao10} considered the more general assumption for $\cA$ that there exists some numbers $(a_{k}^j)$ such that $a_{k}^j T - \E_{\mu}[T_k^j(T)] = o(T^\alpha)$ whereas in Definition~\ref{def:5:DecentralizedUniformEfficiency} we make the choice $a_{k}^j = 1/M$.
Our result could be extended to this case, but we chose to keep the notation simple and focus on \emph{fair allocation} of the optimal arms between players.

@@

% \vspace*{-15pt}  % XXX remove if problem
\begin{lemma}\label{lem:5:1stUpperBound}
\begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
  The term \ref{eq:5:term2} in Lemma~\ref{lem:5:DecompositionRegret} is upper bounded as
  % \hfill{}
  % (Proved in Appendix~\ref{proof:5:1stUpperBound})
  %
  \begin{equation}\label{eq:5:1stUpperBound}
    \ref{eq:5:term2} \leq (\mu_1^* - \mu_M^*) \Bigl(    \sum_{k \in \Mworst} \E_{\mu}[T_k(T)]
    + \sum_{k \in \Mbest} \E_{\mu}[C_{k}(T)]
    \Bigr).
  \end{equation}
  % \vspace*{-5pt}  % XXX
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}

\begin{smallproof}
  Recall that we want to upper bound
  $ \ref{eq:5:term2} : = \sum_{k \in \Mbest} (\mu_k - \mu_{M*}) \left(T - \E_{\mu}[T_k(T)]\right)$.
  First, we observe that, for all $k\in \Mbest$,
  \begin{eqnarray*}
    T - \E_{\mu}[T_k(T)] & \leq T - \E_{\mu}\left[\sum_{t=1}^T \indic(\exists j : A^j(t) = k)\right] \\
    & = \E_{\mu}\left[\sum_{t=1}^T \indic(\forall j, A_j(t) \neq k)\right] = \E_{\mu}\left[\sum_{t=1}^T \indic(k \notin \widehat{S}_t)\right],
  \end{eqnarray*}
  where we denote by $\widehat{S}_t = \{A^j(t), j \in [M]\}$ the set of selected arms at time $t$ (with no repetition). With this notation one can write
  \begin{eqnarray*}
  \ref{eq:5:term2} & \leq & (\mu_1 - \mu_{M^*})  \sum_{k \in \Mbest} \left(T - \E_{\mu}[T_k(T)]\right) \leq  (\mu_1 - \mu_{M^*})  \E_{\mu}\left[\sum_{k \in \Mbest} \sum_{t = 1}^T \indic(k \notin \widehat{S}_t)\right] \\
  & = &  (\mu_1 - \mu_{M^*})  \E_{\mu}\left[ \sum_{t = 1}^T \sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)\right].
  \end{eqnarray*}
  The quantity $\sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)$ counts the number of optimal arms that have not been selected at time $t$. For each mis-selection of an optimal arm, there either exists a sub-optimal arm that has been selected, or an arm in $\Mbest$ on which a collision occurs. Hence
  \[\sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t) = \sum_{k \in \Mbest}\indic(C_k(t)) + \sum_{k \in \Mworst} \indic(\exists j : A^j(t) = k),\]
  which yields
  \[\E_{\mu}\left[ \sum_{t = 1}^T \sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)\right] \leq \sum_{k \in \Mbest}\E_{\mu}\left[\cC_k(T)\right] + \sum_{k \in \Mworst} \E_{\mu}\left[T_k(T)\right]\]
  and Lemma~\ref{lem:5:1stUpperBound} follows.
\end{smallproof}

>>>>

We introduce additional notations in the following definition.
%
\begin{definition}\label{def:5:nbSelections_nbCollisions}
\begin{leftbar}[defnbar]  % XXX leftbar defnbar, comment if needed
  % [$N_k(T)$ and $\cC_k(T)$]
  % \label{def:5:nbSelections}
  Let $N_k^j(T) \eqdef \sum_{t=1}^T \indic(A^j(t) = k)$,
  and denote $N_k(T) \eqdef \sum_{j=1}^M N_k^j(T)$ the \emph{number of selections} of arm $k\in[K]$ by any player $j\in[M]$, up to time $T$.
  % and $\cC_k(T)$ be the number of collisions on arm $k$ up-to time $T$.
% \end{definition}

@@

\begin{lemma}\label{lem:5:DecompositionRegret}
\begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
  For any bandit instance $\boldsymbol{\mu}\in\cP_M$ such that $\mu_M^* > \mu_{M+1}^*$, it holds that
  % \vspace*{-5pt}  % XXX
  % \begin{small}
    \begin{align}\label{eq:5:termeundeuxtermetrois}
      R_T(\boldsymbol{\mu}, M, \cA) &=
      \underbrace{\sum_{k \in \Mworst} (\mu_M^* -  \mu_k) \E_{\mu}[N_k(T)]}_{\emph{\mytag{(a)}{eq:5:term1}}} \\
      & \;\;\;\;\;\;
      + \;\; \underbrace{\sum_{k \in \Mbest} (\mu_k -  \mu_M^*) (T - \E_{\mu}[N_k(T)])}_{\emph{\mytag{(b)}{eq:5:term2}}}
      + \;\; \underbrace{\sum_{k=1}^{K} \mu_k \E_{\mu}[\cC_k(T)]}_{\emph{\mytag{(c)}{eq:5:term3}}}. \nonumber
    \end{align}
  % \end{small}
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}

@@

  Using the definition of regret $R_T(\boldsymbol{\mu}, M, \cA)$ from \eqref{eq:5:regret}, denoted here $R_T$, and this collision indicator $\eta^j(t) \eqdef \indic(\overline{C^j(t)})$,

@@

    R_T

@@

      - \sum_{k=1}^{K} \sum_{j=1}^{M} \mu_k \E_{\mu}\left[ N_k^j(T) \right]

@@

    \intertext{For the first term, we have $T M = \sum\limits_{k=1}^{K} \sum\limits_{j=1}^{M} \E_{\mu}\left[ N_k^j(T)\right]$, and if we denote $\overline{\mu}^* \eqdef \frac{1}{M} \sum\limits_{j \in \Mbest} \mu_j$ the average mean of the $M$-best arms, then,}

@@

    &= \sum_{k=1}^{K} \sum_{j=1}^{M} (\overline{\mu}^* - \mu_k) \E_{\mu}\left[ N_k^j(T) \right]

@@

    &= \sum_{k \in \Mbest\setminus\{M\}} \overline{\Delta_k} \E_{\mu}\left[ N_k(T) \right]
      + \overline{\Delta_{M^*}} \E_{\mu}\left[ N_{M^*}(T) \right] \\
      &\;\;\;\;\;\;\;\; + \sum_{k \in \Mworst} \overline{\Delta_k} \E_{\mu}\left[ N_k(T) \right]

@@

    \intertext{But for $k = M^*$, $N_{M^*}(T) = T M^* - \sum\limits_{k \in \Mbest\setminus\{M\}} \E_{\mu}\left[ N_k(T) \right] - \sum\limits_{k \in \Mworst} \E_{\mu}\left[ N_k(T) \right]$, so by recombining the terms, we obtain,}

@@

    &= \sum_{k \in \Mbest\setminus\{M\}} (\overline{\Delta_k} - \overline{\Delta_{M^*}}) \E_{\mu}\left[ N_k(T) \right]

@@

      &\;\;\;\;\;\;\;\; + \sum_{k \in \Mworst} (\overline{\Delta_k} - \overline{\Delta_{M^*}}) \E_{\mu}\left[ N_k(T) \right]

@@

    R_T
    &= \sum_{k \in \Mbest} (\mu_{M^*} - \mu_k) \E_{\mu}\left[ N_k(T) \right]

@@

      &\;\;\;\;\;\;\;\; + \sum_{k \in \Mworst} (\mu_{M^*} - \mu_k) \E_{\mu}\left[ N_k(T) \right]

@@

  R_T
    & = \sum_{k \in \Mbest} (\mu_k - \mu_{M^*}) \left(T - \E_{\mu}\left[ N_k(T) \right]\right) \\
      & \;\; + \sum_{k \in \Mworst} (\mu_{M^*} - \mu_k) \E_{\mu}\left[ N_k(T) \right]

@@

The regret decomposition in Lemma~\ref{lem:5:DecompositionRegret} is valid for both centralized and decentralized algorithms.
For centralized algorithms, due to the absence of collisions, \ref{eq:5:term3} is obviously zero, and \ref{eq:5:term2} is non-negative, as $N_k(T) \leq T$. For decentralized algorithms, \ref{eq:5:term3} may be significantly large, and term \ref{eq:5:term2} may be negative, as many collisions on arm $k$ may lead to $N_k(T) > T$ (which is counter intuitive with such notations).
However, a careful manipulation of this decomposition shows that the regret is always lower bounded by term \ref{eq:5:term1}.
The Figure~\ref{fig:5:MP__M9_K9_T10000_N1000__9_algos__main_RegretCentralized____env6} in Appendix illustrate two cases of $M<K$ and $M=K$ and the different impact of the three terms (\ref{eq:5:term1}, \ref{eq:5:term2} and \ref{eq:5:term3}) on the regret.

\begin{lemma}\label{lem:5:1stLowerBound}
\begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
    For any strategy $\cA$ and $\boldsymbol{\mu}\in\cP_M$, it holds that
    \begin{align*}
        R_T(\boldsymbol{\mu}, M, \cA)    \geq \sum\limits_{k \in \Mworst} (\mu_M^*- \mu_k) \E_{\mu}[N_k(T)].
    \end{align*}
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}

\begin{smallproof}
  Note that term \ref{eq:5:term3} is clearly lower bounded by $0$
  but it is not obvious for \ref{eq:5:term2} as there is no reason for $N_k(T)$ to be upper bounded by $T$.
  %
  Let $N_k^{!}(T) \eqdef \sum_{t=1}^{T} \indic(\exists! j, A^j(t)=k)$,
  where the notation $\exists!$ stands for ``there exists a unique''.
  Then $N_k(T) = \sum_{t=1}^{T} \sum_{j=1}^{M} \indic(A^j(t) = k)$ can be decomposed as
  \begin{equation*}
    N_k(T) = \sum_{t=1}^{T} \indic(\exists! j, A^j(t) = k) + \sum_{t=1}^{T} \sum_{j=1}^{M} c_{k,t} \indic(A^j(t) = k)
    = N_k^{!}(T) + C_k(T).
  \end{equation*}
  By focusing on the two terms $\ref{eq:5:term2} + \ref{eq:5:term3}$ from the decomposition of $R_T(\boldsymbol{\mu}, M, \cA)$ from Lemma~\ref{lem:5:DecompositionRegret}, we have
  \begin{align*}
    \ref{eq:5:term2} + \ref{eq:5:term3} &=
    \sum_{k \in \Mbest} (\mu_k - \mu_M^*) (T - \E_{\mu}[N_k^!(T)])
    + \sum_{k \in \Mbest} \mu_M^* \E_{\mu}[C_k(T)] \\
    & \;\;\;\;\;\; + \sum_{k=1}^{M} \mu_k \E_{\mu}[C_k(T)]
    - \sum_{k \in \Mbest} \mu_k \E_{\mu}[C_k(T)] \\
    &=
    \sum_{k \in \Mbest} (\mu_k - \mu_M^*) (T - \E_{\mu}[N_k^!(T)])
    + \sum_{k \in \Mbest} \mu_M^* \E_{\mu}[C_k(T)]
    + \sum_{k \in \Mworst} \mu_k \E_{\mu}[C_k(T)] \\
    &=
    \sum_{k \in \Mbest} (\mu_k - \mu_M^*) (T - \E_{\mu}[N_k^!(T)])
    + \sum_{k=1}^{M} \min(\mu_M^*, \mu_k) \E_{\mu}[C_k(T)].
  \end{align*}
  And now both terms are non-negative, as $N_k^!(T) \leq T$, $\min(\mu_M^*, \mu_k)\geq 0$, and $C_k(T) \geq 0$, so $\ref{eq:5:term2} + \ref{eq:5:term3} \geq 0$
  which proves that $R_T(\boldsymbol{\mu}, M, \cA) \geq \ref{eq:5:term1}$, as wanted.
\end{smallproof}

@@

\begin{definition}\label{def:5:DecentralizedUniformEfficiency}
\begin{leftbar}[defnbar]  % XXX leftbar defnbar, comment if needed
  An algorithm $\cA$  is \emph{\textbf{strongly uniformly efficient}} if for all $\boldsymbol{\mu} \in \cP_M$ and for all $\alpha \in (0,1)$,
  % \vspace*{-5pt}  % XXX
  \begin{align}
    & R_T(\boldsymbol{\mu},M,\cA) \mathop{=}\limits_{T \to +\infty} o(T^\alpha) \\
    \text{and} & \;
    \forall j \in [M], k \in \Mbest, \;\;
    % a_{j,k}
    \frac{T}{M}
    - \E_{\mu}[N_k^j(T)] \mathop{=}\limits_{T \to +\infty} o(T^{\alpha}).
    \label{eq:5:SUE}
  \end{align}
\end{leftbar}  % XXX leftbar defnbar, comment if needed
\end{definition}

Having a small regret on every problem instance, \ie, being uniformly efficient,
is a natural assumption,
that rules out algorithms tuned to perform well on specific instances only (\eg, fixed-armed algorithms).
%
From this assumption $\left(R_T(\boldsymbol{\mu},M,\cA)=o(T^\alpha)\right)$ and the decomposition of Lemma~\ref{lem:5:DecompositionRegret} one can see\footnote{With some arguments used in the proof of Lemma~\ref{lem:5:1stLowerBound} to circumvent the fact that \ref{eq:5:term2} may be negative.} that for every $k \in \Mbest$,
${T}- \E_{\mu}[N_k(T)] {=} o(T^{\alpha})$, and so
\begin{equation}\label{eq:5:intermediate}
  % \vspace*{-5pt}  % XXX
  \sum_{j =1}^M\left(\frac{T}{M} - \E_{\mu}[N_k^j(T)]\right) = o(T^{\alpha}).
  % \vspace*{-5pt}  % XXX
\end{equation}

The additional assumption in \eqref{eq:5:SUE} further implies some notion of \emph{fairness}, as it suggests that each of the $M$ players spends on average the same amount of time on each of the $M$ best arms. Note that this assumption is satisfied by any strategy that is invariant under every permutation of the players, \ie, for which the distribution of the observations under $\cA_{\sigma} = (\cA_{\sigma(1)},\dots,\cA_{\sigma(M)})$ is independent from the choice of permutation $\sigma \in \Sigma_M$ of the set $\{1,\dots,M\}$.
In that case, it holds that  $\E_{\mu}[N_k^j(T)]=\E_{\mu}[N_k^{j'}(T)]$ for every arm $k$ and $(j,j') \in [M]$, hence \eqref{eq:5:SUE} and \eqref{eq:5:intermediate} are equivalent, and strong uniform efficiency is equivalent to standard uniform efficiency.
Note that the algorithms studied in Section~\ref{sec:5:algorithms} are permutation invariant, and \MCTopM-\klUCB{} is thus an example of strongly uniformly efficient algorithm, as we prove in Section~\ref{sec:5:upperbounds} that its regret is logarithmic on every instance $\mu \in \cP_M$.

@@

\begin{theorem}\label{thm:5:BetterLowerBound}
\begin{leftbar}[theorembar]  % XXX leftbar theorembar, comment if needed
  Under observation models $\modelun$ and $\modeldeux$, consider a strongly uniformly efficient \emph{decentralized} policy $\cA=(\cA_1,\dots,\cA_M)$ and a problem $\boldsymbol{\mu}\in\cP_M$.
  Furthermore, if $\cA_j$ satisfies $\cI_{\bm{\mu},\bm{\lambda}}(\cA_j,T) = \smallO{\log(T)}$, then
  % \vspace*{-10pt}  % XXX
  \begin{equation}\label{eq:5:LBDraws}
    \forall j \in [M], \ \forall k \in \Mworst, \ \ \ \liminf_{T\to \infty} \frac{\E_{\mu}[N_k^j(T)]}{\log(T)} \geq \frac{1}{\kl(\mu_k, \mu_M^*)}.
  \end{equation}

@@

Observe that the regret lower bound \eqref{eq:5:ourLowerBound} is tighter than the state-of-the-art lower bound in this setup
given by \cite{Zhao10}, that states that
\begin{equation}\label{eq:5:Zhao10LowerBound}
  \mathop{\lim\inf}\limits_{T \to +\infty} \frac{R_T(\boldsymbol{\mu}, M, \cA)}{\log(T)}
  \geq \sum_{k \in \Mworst} \left( \sum_{j=1}^{M} \frac{(\mu_M^* -  \mu_k)}{\kl(\mu_k, \mu_{j}^*)} \right),
\end{equation}
as for every $k \in \Mworst$ and $j \in [M]$, $\kl(\mu_k, \mu_j^*) \geq \kl(\mu_k, \mu_M^*)$
(see Figure~\ref{fig:5:CompLowerBounds} in Appendix~\ref{app:5:illustrationLowerBound}).
%
It is worth mentioning that \cite{Zhao10} considered the more general assumption for $\cA$ that there exists some numbers $(a_{k}^j)$ such that $a_{k}^j T - \E_{\mu}[N_k^j(T)] = o(T^\alpha)$ whereas in Definition~\ref{def:5:DecentralizedUniformEfficiency} we make the choice $a_{k}^j = 1/M$.
Our result could be extended to this case, but we chose to keep the notation simple and focus on \emph{fair allocation} of the optimal arms between players.

@@

% \vspace*{-15pt}  % XXX remove if problem
\begin{lemma}\label{lem:5:1stUpperBound}
\begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
  The term \ref{eq:5:term2} in Lemma~\ref{lem:5:DecompositionRegret} is upper bounded as
  % \hfill{}
  % (Proved in Appendix~\ref{proof:5:1stUpperBound})
  %
  \begin{equation}\label{eq:5:1stUpperBound}
    \ref{eq:5:term2} \leq (\mu_1^* - \mu_M^*) \Bigl(    \sum_{k \in \Mworst} \E_{\mu}[N_k(T)]
    + \sum_{k \in \Mbest} \E_{\mu}[C_{k}(T)]
    \Bigr).
  \end{equation}
  % \vspace*{-5pt}  % XXX
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}

\begin{smallproof}
  Recall that we want to upper bound
  $ \ref{eq:5:term2} : = \sum_{k \in \Mbest} (\mu_k - \mu_{M*}) \left(T - \E_{\mu}[N_k(T)]\right)$.
  First, we observe that, for all $k\in \Mbest$,
  \begin{eqnarray*}
    T - \E_{\mu}[N_k(T)] & \leq T - \E_{\mu}\left[\sum_{t=1}^T \indic(\exists j : A^j(t) = k)\right] \\
    & = \E_{\mu}\left[\sum_{t=1}^T \indic(\forall j, A_j(t) \neq k)\right] = \E_{\mu}\left[\sum_{t=1}^T \indic(k \notin \widehat{S}_t)\right],
  \end{eqnarray*}
  where we denote by $\widehat{S}_t = \{A^j(t), j \in [M]\}$ the set of selected arms at time $t$ (with no repetition). With this notation one can write
  \begin{eqnarray*}
  \ref{eq:5:term2} & \leq & (\mu_1 - \mu_{M^*})  \sum_{k \in \Mbest} \left(T - \E_{\mu}[N_k(T)]\right) \leq  (\mu_1 - \mu_{M^*})  \E_{\mu}\left[\sum_{k \in \Mbest} \sum_{t = 1}^T \indic(k \notin \widehat{S}_t)\right] \\
  & = &  (\mu_1 - \mu_{M^*})  \E_{\mu}\left[ \sum_{t = 1}^T \sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)\right].
  \end{eqnarray*}
  The quantity $\sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)$ counts the number of optimal arms that have not been selected at time $t$. For each mis-selection of an optimal arm, there either exists a sub-optimal arm that has been selected, or an arm in $\Mbest$ on which a collision occurs. Hence
  \[\sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t) = \sum_{k \in \Mbest}\indic(C_k(t)) + \sum_{k \in \Mworst} \indic(\exists j : A^j(t) = k),\]
  which yields
  \[\E_{\mu}\left[ \sum_{t = 1}^T \sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)\right] \leq \sum_{k \in \Mbest}\E_{\mu}\left[\cC_k(T)\right] + \sum_{k \in \Mworst} \E_{\mu}\left[N_k(T)\right]\]
  and Lemma~\ref{lem:5:1stUpperBound} follows.
\end{smallproof}

This result can also be used to recover Proposition~1 from \cite{Anandkumar11}, giving an upper bound on the regret that only depends on
the \emph{expected number of sub-optimal selections} -- $\E_{\mu}[N_k(T)]$ for $k \in \Mworst$ --
and the \emph{expected number of colliding players on the optimal arms} -- $\E_{\mu}[\cC_k(T)]$ for $k \in \Mbest$. Note that, in term (c) the number of colliding players on the sub-optimal arm $k$ may be upper bounded as $\E_{\mu}[\cC_k(T)] \leq M \E_{\mu}[N_k(T)]$.
%
